\documentclass[11pt,letterpaper]{article}

\def\myauthor{Matthew E. Black}
\def\mytitle{vita}
\def\myemail{ejrx@outlook.com}
\def\myweb{http://ejrx.github.io}
\def\myphone{973-975-3366}
\def\mykeywords{
  resume, 
  vita, 
  curriculum vita, 
  cv, 
  matt, 
  ejrx
}

\setlength\parindent{0pt}

\newenvironment{itemize*}%
{\begin{itemize}%
  \setlength{\itemsep}{0pt}}%
{\end{itemize}}

\usepackage{url}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{enumitem}
\setlist{nolistsep,leftmargin=0.15in}
\usepackage[log-declarations=false]{xparse}
\usepackage[urw-garamond]{mathdesign}
\usepackage[no-math]{fontspec}
\usepackage{microtype}
\usepackage[margin=1in,top=1.125in,right=1in,left=2in]{geometry}
\usepackage[strict]{changepage}
\usepackage[
  ocgcolorlinks,
  urlcolor={[rgb]{0,0,0.54}},
  unicode,
  plainpages=false,
  pdfpagelabels,
  pdftitle={\mytitle},
  pdfauthor={\myauthor},
  pdfkeywords={\mykeywords}
]{hyperref}

% fix ocgcolor link breaking; thanks due to Benjamin Lerner (http://goo.gl/VZKR7M)
\makeatletter
\AtBeginDocument{%
  \newlength{\temp@x}%
  \newlength{\temp@y}%
  \newlength{\temp@w}%
  \newlength{\temp@h}%
  \def\my@coords#1#2#3#4{%
    \setlength{\temp@x}{#1}%
    \setlength{\temp@y}{#2}%
    \setlength{\temp@w}{#3}%
    \setlength{\temp@h}{#4}%
    \adjustlengths{}%
    \my@pdfliteral{\strip@pt\temp@x\space\strip@pt\temp@y\space\strip@pt\temp@w\space\strip@pt\temp@h\space re}}%
  \ifpdf
    \typeout{In PDF mode}%
    \def\my@pdfliteral#1{\pdfliteral page{#1}}% I don't know why % this command...
    \def\adjustlengths{}%
  \fi
  \ifxetex
    \def\my@pdfliteral #1{\special{pdf: literal direct #1}}% isn't equivalent to this one
    \def\adjustlengths{\setlength{\temp@h}{-\temp@h}\addtolength{\temp@y}{1in}\addtolength{\temp@x}{-1in}}%
  \fi%
  \def\Hy@colorlink#1{%
    \begingroup
      \ifHy@ocgcolorlinks
        \def\Hy@ocgcolor{#1}%
        \my@pdfliteral{q}%
        \my@pdfliteral{7 Tr}% Set text mode to clipping-only
      \else
        \HyColor@UseColor#1%
      \fi
  }%
  \def\Hy@endcolorlink{%
    \ifHy@ocgcolorlinks%
      \my@pdfliteral{/OC/OCPrint BDC}%
      \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
      \my@pdfliteral{F}% Fill clipping path (the url's text) with current color
      \my@pdfliteral{EMC/OC/OCView BDC}%
      \begingroup%
        \expandafter\HyColor@UseColor\Hy@ocgcolor%
        \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
        \my@pdfliteral{F}% Fill clipping path (the url's text) with \Hy@ocgcolor
      \endgroup%
      \my@pdfliteral{EMC}%
      \my@pdfliteral{0 Tr}% Reset text to normal mode
      \my@pdfliteral{Q}%
    \fi
    \endgroup
  }%
}
\makeatother
% end fixes

\newcommand{\ML}{\textsc{Matlab}}

\newcommand{\mhead}[1]{\leavevmode\marginpar{\sffamily\footnotesize #1}}
\newcommand{\rdate}[1]{{ \hfill #1}}
\renewcommand{\date}[1]{{#1}}
\renewcommand{\labelitemi}{-} 

\setmainfont[
  BoldFont={GaramondNo8 Medium},
]{GaramondNo8}
\setsansfont[
  Color=660000,
]{GaramondNo8}
\setmonofont[Scale=0.85]{FontAwesome}

\makeatletter % fix for \hrulefill w/ mathdesign package
\def\hrulefill{\leavevmode\leaders \hrule height \rulethickness \hfill\kern\z@}
\makeatletter

\begin{document}\flushbottom
\pagestyle{fancy} \setlength\headwidth{6.5in}
\rhead{\textsc{\myauthor—R\'{e}sum\'{e}—\thepage{} of \pageref*{LastPage}}} \cfoot{}
\thispagestyle{empty}
\begin{adjustwidth}{-1in}{}
{\Huge
  {\textsc{%
    {M}\kern-1.5ptatthew
    {E}\kern-2pt.~%
    {Black}
  }}
}
\hfill\hfill\hfill
{
  \begin{minipage}[b]{2in}
    \flushleft \footnotesize 
    28 Alpine Drive \\  
    Denville, NJ~~07834
  \end{minipage}
  \hfill
  \begin{minipage}[b]{1.2in}
    \flushright \footnotesize 
    \href{tel:\myphone}{\myphone} \\ %\texttt{}~
    \href{mailto:\myemail}{\myemail} \\
    \href{\myweb}{\myweb} \\
  \end{minipage}
}\par
\hrulefill
\end{adjustwidth}  
\reversemarginpar 
\setlength\marginparwidth{0.85in}
\smallskip
\mhead{Education}%
\textbf{University of Maryland,} College Park, MD \newline
\emph{Bachelor of Science, \href{http://bioe.umd.edu/}{Bioengineering}} \rdate{2009–2013}
\begin{itemize*}
  \item Cumulative GPA: 3.98/4.00; \emph{Magna Cum Laude}.
  \item Capstone Project: Tracheal Occlusion STENTSOR Technology
\end{itemize*}

\bigskip
\mhead{Research \newline Experience}%
\textbf{Control of Miniaturized Systems Lab,} College Park, MD \newline
\emph{Undergraduate Research Assistant} \rdate{2012-2013}
\begin{itemize*}
\item Developed image processing and data analysis programs for tracking nanoparticle movement through \emph{ex vivo} tissue samples.
\item Designed and fabricated a system to orient and cool an array of electromagnets used to control nanoparticle movements in tissues.
\end{itemize*}

\medskip
\textbf{Children's National Medical Center,} Washington, DC \newline
\emph{Senior Academic Associate} \rdate{2012-2013}
\begin{itemize*}
\item Coordinated research activities for a phase-II clinical drug trial. While coordinator, CNMC was the top-enrolling study site, nationwide.
\item Assisted with data management and patient recruitment for clinical trials in the Emergency Department.
\end{itemize*}

\medskip
\textbf{Soft Materials Laboratory,} Hoboken, NJ \newline
\emph{Undergraduate Research Assistant} \rdate{2012–2012}
\begin{itemize*}
\item Developed a method for synthesizing PDMS-silica nanocomposite gels for use in thermovoltaics research.
\item Conducted and co-designed experiments examining the kinetics of the ``coffee ring effect'' in polymer solutions with colloidal suspensions.
\end{itemize*}

\bigskip
\mhead{Professional \newline Experience}%
\textbf{Memorial Sloan Kettering Cancer Center,} New York, NY \newline
\emph{Data Analyst} \rdate{\textsc{Dec}~2014–\textsc{Present}}
\begin{itemize*}
  \item Develop and maintain backend database and data-access code for the hospital's internal quality assurance website, \href{http://mskcc.org/amplio-system}{Amplio}.
  \item Create software solutions, as part of the \href{http://mskcc.org/research-advantage/core-facilities/web-survey-core}{WebCore} team, for the collection and analysis of patient-reported outcomes.
\end{itemize*}

\medskip
\textbf{Spoon.net,} Seattle, WA \newline
\emph{Program Manager Associate} \rdate{2013–2014}
\begin{itemize*}
\item Created, developed and led the management of Spoon's \href{http://seleniumhq.org}{Selenium}-based automated browser testing service.
\end{itemize*}

\bigskip
\mhead{Software \newline Proficiencies}%
\emph{Working knowledge}\newline%—comfortable using in a professional setting
C\#,
\ML{}/Octave,
Python,
R,
SQL,
HTML/CSS,
\LaTeX{}

\medskip
\emph{Basic knowledge}\newline%—would require some training/use to refresh my memory
C,
Cadence PSpice,
Coq,
Haskell,
LabView,
SolidWorks

\bigskip
\mhead{Publications}%
\par\vspace{-\baselineskip}E. Senses, \textbf{Black, M.}, T. Cunningham, S.A. Sukhishvili, \& P. Akcora~(\date{2013}).
\href{}{Spatial ordering of colloids in a drying aqueous polymer droplet}. \emph{Langmuir}, 2013, 29(8) 2588-2594.
\end{document}
